First, I would like to thank my committee chair Eyal Amiran for his support, guidance and mentorship throughout this project. His deep intellectual engagement with my writing, his constant encouragement and advice while seeing this dissertation through to completion and his genuine interest in my well-being and future success all deserve my most profound gratitude. I also thank my committee members, James Steintrager, whose seminars in critical theory and constructivism sparked a deep theoretical engagement that runs throughout this project and beyond, and David Theo Goldberg, who not only contributed great insights to my work but also exemplifies the critically engaged public intellectual to which I aspire. Kavita Philip also deserves special mention for encouraging my interest in technoculture and for teaching me how to engage technology as political. A number of additional faculty also supported my project in various ways throughout its intellectual formation, including Ackbar Abbas, Paul Dourish, Jonathan Hall, Dina Al-Kassim, the late Mark Poster, and Rei Terada.

Thanks to Mark Pangilinan and Jacqueline Way, who organized a dissertation colloquium in 2013 that allowed me to present and refine an early chapter draft. Several grad school friends and colleagues helped significantly shape my academic voice over the years through ongoing conversations and collaborations, including Josef Nguyen, Matthew Schilleman, Rob Schoenbeck, and Ken Yoshida.

I have enjoyed enormous flexibility and understanding from my employers throughout my tenure as a hybrid humanities grad student and software engineer, for which I thank Alexandre and Xavier Kral at Javaground, Curt Bererton and Vijay Myneni at ZipZapPlay/PopCap, and Hadi Partovi and Mona Akmal at Code.org. 

UCI generously provided two year-long fellowships during my graduate tenure. The UC Humanities Research Institute provided fellowships to attend the summer Seminar in Experimental Critical Theory in 2006 and 2011, both of which were formative experiences. Graduate program coordinators Bindya Baliga and Arielle Read both provided indispensable assistance in navigating university bureaucracy on my behalf.

I am eternally grateful to my brothers and parents for their intellectual and moral support. Finally, my greatest thanks goes to Jenelle Wagner, who proofread my drafts, organized my scattered thoughts, gave me the strength to press on and filled my long dissertation-writing days with love and laughter. None of this would have been at all possible without her.